Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny

### 2018-05-17 tex/manuscript.tex
added rough conclusion section

>>>>

\section*{Conclusions}
	With the characterization of the four herein described species, the Entimine genus \textit{Minyomerus} has expanded to include a total of 21 species.
	We opine there is a strong likelihood that additional undescribed species exist throughout the North American deserts, given the endemicity of many members of the genus.
	Furthermore, we believe that sampling in poorly-sampled locales, particularly in the northwestern United States and in northern Mexico, will yield new species and inferences into the evolutionary history of this genus.
	Acquisition of specimens suitable for DNA extraction would be invaluable for generating a molecular phylogeny of this genus for comparison with our analysis.
	We indicate a possible origin of \textit{Minyomerus} in central Mexico based on their current distribution; however, it is currently not possible to test this hypothesis due to a lack of fossils and molecular clock.
	Additionally, we identify a significant gap in our understanding of the reproductive behavior of certain species we suspect to be parthenogenetic.
	Future efforts could be targeted towards rearing and karyotyping specimens of these species to assess their reproductive biology in this context.
	Finally, the validity of \textit{Minyomerus} as a member of the Tanymecini and its relationships to other Entimine taxa remain uncertain.
	We therefore emphasize the need for further taxonomic treatment of broad-nosed weevils to resolve these questions.
